Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-22 paper/paper.Rmd
Add short discussion & references for BF

We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level. Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value. The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.

@@

### Original ES in the confidence interval of the replication

We determine whether the original reported effect size is included in the 95\% confidence interval found in the replication studies.

### Bayes factor analysis

Next, following @etz2016, we conducted a Bayesian analysis.

>>>>

@@

We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level. Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value. The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective. While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates. This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included.

### Bayes factor and effect size analysis

Next, following @etz2016, we compared Bayes Factors between the original and replication. The Bayes Factor is an alternative to classical null hypothesis significance testing; it quantifies the evidence in favor of a hypothesis as the ratio of the likelihood of the data under that hypothesis relative to another [@jeffreys1961]. Its proponents point to many advantages over classical $p$-values. For example, it does not privilege the null hypothesis and can provide evidence either *for* or *against* it [see also @scheibehenne2016, @wagenmakers2016]. While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
